Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-03-16 code/paper.Rmd
circle chord plot

ggplot(revision_history_page_details_ip_addresses_countries, 
       aes(sum_prop_internal, 
           prop_anon_of_all_edits)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  theme_minimal()

>>>>

```{r}
adjacency_list_3_cols <- 
revision_history_page_details_ip_addresses_df %>% 
  filter(!is.na(Country),
         !is.na(country_name)) %>% 
  group_by(Country, country_name) %>% 
  count() %>% 
  rename(to = Country,
         from = country_name,
         value = n) %>% 
  ungroup() %>% 
  mutate(from = ifelse(from == "Hashemite Kingdom of Jordan", "Jordan", from)) %>% 
  select(from, to , value) %>% 
  filter(value > 100) %>% 
  left_join( revision_history_page_details_ip_addresses_df %>% 
               select(country_name, continent_name) %>% 
               distinct(),
             by = c('from' = 'country_name')) %>% 
  arrange(continent_name,  from, to)

adjacency_list <- 
adjacency_list_3_cols%>% 
  select(-continent_name)

get_countries_in_continent <- function(x) {

  xx <- 
  revision_history_page_details_ip_addresses_df %>% 
    select(country_name, continent_name) %>% 
    filter(continent_name == x) %>% 
    pull(country_name) %>% 
    unique()

  xx[
 unique( c(adjacency_list$from,
           adjacency_list$to))
 ]
}

africa   <- get_countries_in_continent("Africa")        
asia    <- get_countries_in_continent("Asia")       
europe  <-get_countries_in_continent("Europe")  
north_america  <- get_countries_in_continent("North America")         
oceania <-  get_countries_in_continent("Oceania") 
south_america  <-  get_countries_in_continent("South America")

library(circlize)
circos.clear()
chordDiagram(adjacency_list, 
             directional = 1,
             direction.type = c("diffHeight", "arrows"),
             link.arr.type = "big.arrow", 
             diffHeight = -uh(2, "mm"),
             annotationTrack = "grid", 
             preAllocateTracks = list(track.height = max(0.4)))

# we go back to the first track and customize sector labels
circos.track(track.index = 1, panel.fun = function(x, y) {
    circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index, 
        facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
}, bg.border = NA) # here set bg.border to NA is important

highlight.sector(africa, track.index = 1, col = "#00FF0040", 
    text = "Africa", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(asia, track.index = 1, col = "#0000FF40", 
    text = "Asia", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(europe, track.index = 1, col = "blue", 
    text = "Europe", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(north_america, track.index = 1, col = "orange", 
    text = "North America", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(oceania, track.index = 1, col = "purple", 
    text = "Oceania", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(south_america, track.index = 1, col = "brown", 
    text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)

#-- 
circos.track(track.index = 2, panel.fun = function(x, y) {
    sector.index = get.cell.meta.data("sector.index")
    xlim = get.cell.meta.data("xlim")
    ylim = get.cell.meta.data("ylim")
    circos.text(mean(xlim), mean(ylim), sector.index, cex = 0.6, niceFacing = TRUE)
}, bg.border = NA)

#--
circos.clear()
circos.par(gap.after = rep(c(rep(1, 4), 8), 3))

chordDiagram(adjacency_list, annotationTrack = c("grid", "axis"),
    preAllocateTracks = list(
        track.height = uh(4, "mm"),
        track.margin = c(uh(4, "mm"), 0)
))

circos.track(track.index = 2, panel.fun = function(x, y) {
    sector.index = get.cell.meta.data("sector.index")
    xlim = get.cell.meta.data("xlim")
    ylim = get.cell.meta.data("ylim")
    circos.text(mean(xlim), mean(ylim), sector.index, cex = 0.6, niceFacing = TRUE)
}, bg.border = NA)

highlight.sector(africa, track.index = 1, col = "red", 
    text = "Africa", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(asia, track.index = 1, col = "green", 
    text = "Asia", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(europe, track.index = 1, col = "blue", 
    text = "Europe", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(north_america, track.index = 1, col = "orange", 
    text = "North America", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(oceania, track.index = 1, col = "purple", 
    text = "Oceania", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(south_america, track.index = 1, col = "brown", 
    text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)
